### 2023-06-27 manuscript.tex
ro-crate of this article [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/7252a9e9e0e603e16c53d583f5a2b6ad2a2a60ac.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/7252a9e9e0e603e16c53d583f5a2b6ad2a2a60ac/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5384402598

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/be8675b6907eabfc339d356014312f2b2aa8292e/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/be8675b6907eabfc339d356014312f2b2aa8292e}{stain/2022-fdo-paper@be8675b}
on June 26, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/7252a9e9e0e603e16c53d583f5a2b6ad2a2a60ac/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/7252a9e9e0e603e16c53d583f5a2b6ad2a2a60ac}{stain/2022-fdo-paper@7252a9e}
on June 27, 2023.
